Naturalness in U(1) extensions of the MSSM

### 2014-12-17 paper/e6ssm-tuning-paper.tex
fix a couple of my typos. there will be more.

\section{\label{sec:results}Results}
% Our results. Plots to go in here:
%    - tuning as a function of stop mass for the MSSM and E6SSM
Many recent papers have focussed on light stops as allowing natural
SUSY and there has been a lot of theoretical effort to find SUSY
models with a $125$ GeV Higgs boson while still having light stops
and experimental efforts to search for light stops.  This is entirely
appropriate, however the fine tning problem from the stops depends
crucially on the RG evolution from the GUT scale, since this is how
the squark masses feed into the soft Higgs masses that appear in the
EWSB conditions.

@@

Therefore the tuning in these models depends on less assumptions than
the tuning which concerns people in the MSSM and the owest tuned
models are adderessed directly with $Z^\prime$ searches.

>>>>

\section{\label{sec:results}Results}
% Our results. Plots to go in here:
%    - tuning as a function of stop mass for the MSSM and E6SSM
Many recent papers have focussed on light stops as allowing natural
SUSY and there has been a lot of theoretical effort to find SUSY
models with a $125$ GeV Higgs boson while still having light stops
and experimental efforts to search for light stops.  This is entirely
appropriate, however the fine tuning problem from the stops depends
crucially on the RG evolution from the GUT scale, since this is how
the squark masses feed into the soft Higgs masses that appear in the
EWSB conditions.

@@

Therefore the tuning in these models depends on less assumptions than
the tuning which concerns people in the MSSM and the lowest tuned
models are adderessed directly with $Z^\prime$ searches.
